---
title: "Introduction"
---
```{r, include = FALSE}
leanbuild::set_knitr_image_path()
```

# Introduction

## What Is AnVIL?

AnVIL is NHGRI's Genomic Data Science Analysis, Visualization, and Informatics Lab-Space.  It provides a platform for performing genomic data analysis on the cloud.

<iframe width="560" height="315" src="https://www.youtube.com/embed/XC5qzj-yZb8" title="YouTube video player" frameborder="0" allow="accelerometer; autoplay; clipboard-write; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>

## Does AnVIL Cost Money?

Through AnVIL, you pay for computing resources as you use them.  If you'd like to try it out, new users can claim a $300 Google Cloud credit to test out the platform and perform some small analyses.

We also provide a [cost estimator](https://jhudatascience.org/AnVIL_Book_Getting_Started/pis-and-lab-managers.html#types-of-costs).

## Where Can I Get Help?

Please visit our community support forum at [`help.anvilproject.org`](https://help.anvilproject.org) with any questions (or suggestions!) you may have.

You can also visit the [Getting Started Guide](https://jhudatascience.org/AnVIL_Book_Getting_Started/) and [`anvilproject.org/learn`](https://anvilproject.or/learn) for additional resources.

## Activate `scroll_highlight` Feature {#scroll-highlight}

Note that some sections of this book cover steps in a lot of detail. When navigating the table of contents, you can click subsection (e.g., 2.2, 4.2) headers a second time to expand the table of contents and enable the `scroll_highlight` feature. This can help you follow the separate steps within more clearly.

```{r, echo=FALSE, fig.alt="Double-clicking on the H2 headers (for example, 2.2) will expand the contents for view using the 'scroll_highlight' feature."}
leanbuild::include_slide("https://docs.google.com/presentation/d/18yUr5XSEMgPk8JXFLKfG9JF7L9NpKbCF_mIcXagogKg/edit#slide=id.gde0d2ef5f6_0_1")
```