# (PART\*) Instructor Setup {-}

```{r, include = FALSE}
leanbuild::set_knitr_image_path()
```

# Account Setup

## Overview of Account Setup

AnVIL uses [Terra](https://anvil.terra.bio/) to run analyses. Terra operates on Google Cloud Platform, so you’ll pay for all storage and analysis costs through a Google account linked to Terra. The costs are the standard Google Cloud Platform fees for storing and moving data as well as executing an analysis. These costs are passed along through Terra without any markup.

## Step 1: Create a Google Account {#google-account}

Terra operates on Google Cloud Platform, so you will need a (free) Google account which will allow you to access the Terra platform to manage students and in-class analyses.

Your Google account will also (1) allow you to manage billing yourself or (2) allow a Program Manager to do so on your behalf.

```{r, child=c("_child_create_google_account.Rmd")}

```

## Step 2: Set Up Google Billing

## Step 3: Add Terra to Google Billing Account

## Step 4: Create a Terra Billing Project

## Step 5: Set Up Alerts

## Step 6: Create First Workspace {#first-workspace}

## Wrap-Up
