# (PART\*) Instructor Setup {-}

```{r, include = FALSE}
ottrpal::set_knitr_image_path()
```

# Creating an instructor account

AnVIL uses [Terra](https://anvil.terra.bio/) to run analyses. Terra operates on Google Cloud Platform, so you’ll pay for all storage and analysis costs through a Google account linked to Terra. The costs are the standard Google Cloud Platform fees for storing and moving data as well as executing an analysis. These costs are passed along through Terra without any markup.

## Create a Google Account {#google-account}

Terra operates on Google Cloud Platform, so you will need a (free) Google account which will allow you to access the Terra platform to manage students and in-class analyses.

Your Google account will also (1) allow you to manage billing yourself or (2) allow a Program Manager to do so on your behalf.

```{r, child=c("_child_create_google_account.Rmd")}

```

## Sign in to Terra

You need to sign into Terra to allow Billing Project managers to add you to projects and/or Workspaces. [Launch Terra](https://anvil.terra.bio/#workspaces), and you should be prompted to sign in with your Google account.

You can always access Terra by going to [`anvil.terra.bio`](https://anvil.terra.bio/), or by clicking the link on the AnVIL home page.

```{r, echo=FALSE, fig.alt='Screenshot of the AnVIL home page. The button to "launch Terra" is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1tyt8ifxD3y7QW3nN27jh02aPrBvNEo1GN_u2Ne_UngM/edit#slide=id.gde7783227e_0_31")
```


## Set up Google Billing (some users)

Google Billing Accounts are how you pay Google for you and your students' cloud costs.

Depending on how you are being funded, this may be taken care of for you. If your funding is being managed by a third party (e.g. through a funding mechanism such as [STRIDES](https://datascience.nih.gov/strides), or through your institution), contact them to determine whether you need to do any billing administration through Google.  If not, you can proceed directly to [Terra Billing Projects](#terra-billing-projects).

## Set up Terra Billing Projects {#terra-billing-projects}

Terra Billing Projects are how you grant people permission to compute on AnVIL.  By adding someone to your Billing Project, you enable them to use your funding to carry out activities on AnVIL.

When teaching on AnVIL

- You will need to *manage* members of your Billing Project, in order to add students and TAs.  This is most easily done using Terra Groups.
- You may or may not need to *create* your own Terra Billing Projects.  If your funding is being managed by a third party (e.g. through a funding mechanism such as [STRIDES](https://datascience.nih.gov/strides), or through your institution), contact them to determine whether you should create Terra Billing Projects yourself.

The instructions below walk you through creating a Terra Billing Project.  If you do not need to create your own, you can proceed directly to creating an Instructor / TA Group.


### Create Terra Billing Project(s)

It's often beneficial to set up two separate Billing Projects for a course:

1. Instructor/TA - used to fund development and testing of the material.  It can persist for multiple sessions of the course.
2. Student - funds all student activity, and is deleted at the end of the course activities.

This is not required, but can make management a bit easier.

 

# Creating and adding student accounts

Since Terra operates on Google Cloud Platform, students need a Google account to make sure you can keep track of any computing costs they accrue. 

## Have students create a Google Account

```{r, child=c("_child_create_google_account.Rmd")}

```

## Have students sign in to Terra

Students need to sign into Terra with their Google account to allow you the  instructor to add them to projects and/or Workspaces associated with your specific class. This is the only way students can launch applications and perform computations on AnVIL. Have students [launch Terra](https://anvil.terra.bio/), and they should be prompted to sign in with your Google account.

::: {.warning}
**Collect Accounts**: It is _very important_ students share the Google account they used above with you! Otherwise, you cannot add them to billing projects, groups, or Workspaces.
:::

Students can always access Terra by going to [`anvil.terra.bio`](https://anvil.terra.bio/), or by clicking the link on the AnVIL home page.

```{r, echo=FALSE, fig.alt='Screenshot of the AnVIL home page. The button to "launch Terra" is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1tyt8ifxD3y7QW3nN27jh02aPrBvNEo1GN_u2Ne_UngM/edit#slide=id.gde7783227e_0_31")
```

# Groups for easy management

Groups enable you to share your class Workspace and manage permissions for many people at once. We recommend starting with one Group for instructors and one Group for students.

## Instructor Group {#instructor-group}

Create an informative, unique Group name for any co-instructors and teaching assistants. We suggest a combination of institution-class-role (e.g., “jhu-bmr2021-instructors”). Only letters, numbers, underscores, and dashes are allowed in Group names. To create a Group for instructors:

1. Go to [https://anvil.terra.bio/#groups](https://anvil.terra.bio/#groups)

1. Click “+ Create a New Group”

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page. The "Create a New Group" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_6")
    ```

1. Type in your instructor Group name

1. Click “CREATE GROUP”

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page with Create New Group pop out box. The Group name, jhu-bmr2021-instructors, has been entered and the "CREATE GROUP" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_16")
    ```

You now have a unique **instructor Group**.

### Add Instructors as "Admin" (Instructor Group)

Now that your instructor Group has been created, you should add any additional instructors. You should also ensure that they have the correct permissions. 

1. Go to https://anvil.terra.bio/#groups/ and click on the instructor Group name. This page should also be visible at `https://anvil.terra.bio/#groups/<group-name>`.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group, and the specific Group that was just created. The Group Name is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g10118383b73_193_0")
    ```

1. Click on “+Add User”. You will be prompted to add the instructor’s AnVIL ID. 

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page for the specific Group that was just created. The "+Add User" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_45")
    ```

1. Type in the instructor’s AnVIL ID

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The instructor`s AnVIL ID, instructor-1@gmail.com, has been entered and the AnVIL ID (email) is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_58")
    ```

1. Make sure “Can manage users (admin)” is **selected**

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The instructor`s AnVIL ID, instructor-1@gmail.com, has been entered and the checkbox "Can manage users (admin)" has been selected and is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_65")
    ```

1. Click ADD USER. This will take you back to the Group administration page.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The instructor`s AnVIL ID, instructor-1@gmail.com, has been entered and the "ADD USER" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_71")
    ```

Make sure the newly added instructor displays “Admin” under “Roles” beside their AnVIL ID. Repeat this process for any additional co-instructors and teaching assistants.

```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the instructor Group that was just created, where the newly added instructor is visible in the user list. The instructor`s AnVIL ID, instructor-1@gmail.com is visible next to the role "Admin", which is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_78")
```

## Student Group {#student-group}

Next, you will create a Group for your students. Create an informative, unique Group name. We suggest a combination of institution-class-role (e.g., “jhu-bmr2021-students”). Only letters, numbers, underscores, and dashes are allowed in Group names. To create a Group for students:

1. Go to https://anvil.terra.bio/#groups

1. Click “+ Create a New Group”

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page. The "Create a New Group" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_6")
    ```

1. Type in your student Group name

1. Click “CREATE GROUP”

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page with Create New Group pop out box. The Group name, jhu-bmr2021-students, has been entered and the "CREATE GROUP" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_38")
    ```

You now have a unique **student Group**.

### Add Instructors as "Admin" (Student Group)

The next steps ensure any additional co-instructors and teaching assistants are able to administer the student Group in case you are unavailable. Follow the steps below to add each co-instructor in the student Group:

1. Go to https://anvil.terra.bio/#groups/ and click on the student Group name. This page should be visible at `https://anvil.terra.bio/#groups/<group-name>`.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group, and the specific Group that was just created. The student Group name is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g10118383b73_193_8")
    ```

1. Click on “+Add User”. You will be prompted to add the instructor’s AnVIL ID. 

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page for the specific Group that was just created. The "+Add User" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_104")
    ```

1. Type in the instructor’s AnVIL ID

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The instructor`s AnVIL ID, instructor-1@gmail.com, has been entered and the AnVIL ID (email) is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_58")
    ```

1. Make sure “Can manage users (admin)” is **selected**

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The instructor`s AnVIL ID, instructor-1@gmail.com, has been entered and the checkbox "Can manage users (admin)" has been selected and is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_65")
    ```

1. Click ADD USER. This will take you back to the Group administration page.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The instructor`s AnVIL ID, instructor-1@gmail.com, has been entered and the "ADD USER" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_71")
    ```

Make sure the newly added instructor displays “Admin” under “Roles” beside their AnVIL ID. Repeat this process for any additional co-instructors and teaching assistants.

```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the student Group that was just created, where the newly added instructor is visible in the user list. The instructor`s AnVIL ID, instructor-1@gmail.com is visible next to the role "Admin", which is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_87")
```

### Add Students as "Member"

Follow the steps below to add individual students to the student Group:

1. Go to https://anvil.terra.bio/#groups/ and click on the student Group name. This page should be visible at `https://anvil.terra.bio/#groups/<group-name>`.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group, and the specific Group that was just created. The student Group name is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g10118383b73_193_8")
    ```

1. Click on “+Add User”. You will be prompted to add an AnVIL ID. 

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page for the specific Group that was just created. The "+Add User" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_104")
    ```

1. Type in the student’s AnVIL ID

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The student`s AnVIL ID, student-1@gmail.com, has been entered and the AnVIL ID (email) is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_111")
    ```

1. Click ADD USER

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The student`s AnVIL ID, student-1@gmail.com, has been entered and the "ADD USER" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_117")
    ```

Make sure the newly added student displays “Member” under “Roles” beside their AnVIL ID. At present, each student’s AnVIL ID must be added separately.

```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the student Group that was just created, where the newly added student is visible in the user list. The student`s AnVIL ID, student-1@gmail.com is visible next to the role "Member", which is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_125")
```

Your instructor and student Groups are now set up.

## Group Email Lists

Note that your newly created Groups have Group emails associated with them. Take note of these Group emails. You will use them for granting access to your class Billing Projects and Workspaces. It saves you from having to add or revoke access to students one by one.

```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page. Emails associated with newly formed Groups have been highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_96")
```
