# (PART\*) Running The Class {-}

# Overview {#run-class}

This section describes how to get your students set up to access AnVIL.  These steps will need to be *repeated for each new offering of the course*.

<br>

::: {.notice}
**Notify Terra**

In addition to setting up your class, you may want to contact Terra to [submit a request](https://support.terra.bio/hc/en-us/requests/new) for a hold on scheduled maintenance and downtime.  Contacting Terra ahead of your class time helps the Terra team avoid any major disruptions to your class.  It’s also a good idea to ask about major changes planned for the time prior to your class.
:::

# Set up Funding

As a reminder, Terra Billing Projects are how you grant people, including your students, permission to compute on AnVIL.  By adding someone to your Billing Project, you enable them to use your funding to carry out activities on AnVIL.

You *can* just add students to the same Billing Project that you are using yourself, but we generally recommend creating a separate Billing Project to fund student activity.  This makes it easy to deactivate when the course is over, without freezing your own projects.

Depending on how you are being funded, this may be taken care of for you. If your funding is being managed by a third party (e.g. through a funding mechanism such as [STRIDES](https://datascience.nih.gov/strides), or through your institution), contact them to determine whether you should create a Terra Billing Project for your students.

:::{.warning}
Regardless of who is managing funding, it is essential to make sure that you have permission to create enough Workspaces for all of your students!

To prevent abuse, new users are only permitted to create a few Workspaces.  See [Request Quota Increase](#quota-increase) for more information about how to make sure your students will be able to create Workspaces.
:::

## Create Student Billing Project

**Note:** Terra Billing Projects need unique names.  One option is to use a combination of institution-class-role-term (e.g. `jhu-bio101-students-2023FA`).

To create a Terra Billing Project:

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_terra_billing_project_create.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

::: {.notice}
**Reminder**: It's often a good idea to add at least one other Owner of a Billing Project in order to avoid getting locked out, in case the original owner loses access to their account.  See the section on [adding instructors to a billing project](#add-instructors-billing-project) if you need a reminder on how to do this.
:::

## Request Quota Increase {#quota-increase}

To prevent abuse, new users are only permitted to create a few Workspaces.  If each of your students needs their own Workspace (e.g. they each clone their own copy of a Workspace), you will quickly run into this limit and students will not be able to clone or create new Workspaces.

This limit is imposed by Google, rather than Terra (Google only permits you to create a few Google Cloud "Projects", and each Terra Workspace is a Google Cloud Project), so you will need to contact Google directly to request a "billing quota increase", using [this form](https://support.google.com/code/contact/billing_quota_increase).  This should be done by the owner of the Google Billing Account.  If you set up billing yourself, this is you; otherwise talk to your funding provider and make sure that you have enough Google Cloud Projects available for all your students (typically one per student, unless students need multiple Workspaces).

At the time of writing (Feb 2023) Terra is working to expedite this process for Terra users; we recommend checking the [relevant Terra documentation](https://support.terra.bio/hc/en-us/articles/6101030164507-When-workspace-creation-fails-Google-project-quotas) for the latest information as well as recommendations about how to fill out the form.

In our experience, the process has been reasonably straightforward and quick (approved in a couple of days).

# Create Student Group {#student-group}

Creating a Group for your students will let you easily manage the class as a whole by granting the Group access to Billing Projects and Workspaces.

You will need a unique name for your Group. We suggest a combination of institution-class-role-term (e.g., `jhu-bio101-students-2023FA`). Only letters, numbers, underscores, and dashes are allowed in Group names.

## Create Terra Group

To create a Group:

::::{.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_terra_group_create.Rmd",
  branch = "add-terra-groups-modules",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

You now have a unique **student Group**.

## Add Instructors to Group

Now that your student Group has been created, you should add any additional instructors / course coordinators as **Admins**.  This will give them permission to add and remove students, in case you are unavailable.

::: {.notice}
If you created an instructor Group, you can instead add the *Instructor Group* as an Admin of the *Student Group*.  This will enable everyone in the Instructor Group to act as an Admin for the Student Group.  To do this, you will need the email address associated with the Instructor Group, which can be found on the Group management page: https://anvil.terra.bio/#groups.
:::

To add someone to your group:

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_terra_group_add_member.Rmd",
  branch = "add-terra-groups-modules",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::


# Grant Students Access

The final step is to grant your students permission to access resources (Billing Projects and Workspaces) so that they can launch applications and perform computations on AnVIL.

<br>

::: {.warning}
Make sure you understand when and where your students can spend money!

The following actions will give your students the ability to spend money on AnVIL:

- Adding them to a **Billing Project** - this will let them create their own Workspaces
- Adding them as **Writers or Owners to a Workspace** - this will let them compute in the Workspace
:::

Our recommendation is to **do the following steps ahead of time**:

- Have students create accounts
- Add students to the Student Group
- Give the Student Group access to any Workspaces **as Readers**.  This will let them view the contents of the Workspace but not spend money in it.

**Wait until shortly before the students need to compute** to add the Student Group to the Billing Project.  This prevents them from starting something up early and then accruing costs by failing to shut it down.

## Have Students Create Accounts

Each of your students will need to:

1. Create a Google account, if they do not already have one
2. Sign in to Terra
3. Provide you with their username, so that you can add them to your Student Group

Student-facing instructions for account creation (and several other activities) are provided in the [**Student Instructions**](#student-instructions) section.

## Add Students to Group

## Add Student Group to Workspace(s)

## Add Student Grouop to Billing Project

# Groups for easy management


### Add Students as "Member"

Follow the steps below to add individual students to the student Group:

1. Go to https://anvil.terra.bio/#groups/ and click on the student Group name. This page should be visible at `https://anvil.terra.bio/#groups/<group-name>`.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group, and the specific Group that was just created. The student Group name is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g10118383b73_193_8")
    ```

1. Click on “+Add User”. You will be prompted to add an AnVIL ID. 

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page for the specific Group that was just created. The "+Add User" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_104")
    ```

1. Type in the student’s AnVIL ID

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The student`s AnVIL ID, student-1@gmail.com, has been entered and the AnVIL ID (email) is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_111")
    ```

1. Click ADD USER

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The student`s AnVIL ID, student-1@gmail.com, has been entered and the "ADD USER" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_117")
    ```

Make sure the newly added student displays “Member” under “Roles” beside their AnVIL ID. At present, each student’s AnVIL ID must be added separately.

```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the student Group that was just created, where the newly added student is visible in the user list. The student`s AnVIL ID, student-1@gmail.com is visible next to the role "Member", which is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_125")
```

Your instructor and student Groups are now set up.

## Group Email Lists

Note that your newly created Groups have Group emails associated with them. Take note of these Group emails. You will use them for granting access to your class Billing Projects and Workspaces. It saves you from having to add or revoke access to students one by one.

```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page. Emails associated with newly formed Groups have been highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_96")
```

# Shutting Down
