# (PART\*) Running The Class {-}

# Overview {#run-class}

This section describes how to get your students set up to access AnVIL.  These steps will need to be *repeated for each new offering of the course*.

# Setup Funding

:::{.warning}
Regardless of who is managing funding, it is essential to make sure that you have permission to create enough Workspaces for all of your students!

To prevent abuse, new users are only permitted to create a few Workspaces.  See [Request Quota Increase](#quota-increase) for more information about how to make sure your students will be able to create Workspaces.
:::

## Create Student Billing Project

## Request Quota Increase {#quota-increase}

To prevent abuse, new users are only permitted to create a few Workspaces.  If each of your students need their own Workspace (e.g. they each clone their own copy of a Workspace), you will quickly run into this limit and students will not be able to clone or create new Workspaces.

This limit is imposed by Google, rather than Terra (Google only permits you to create a few Google Cloud "Projects", and each Terra Workspace is a Google Cloud Project), so you will need to contact Google directly to request a "billing quota increase", using [this form](https://support.google.com/code/contact/billing_quota_increase).  This should be done by the owner of the Google Billing Account.  If you set up billing yourself, this is you; otherwise talk to your funding provider and make sure that you have enough Google Cloud Projects available for all your students (typically one per student, unless students need multiple Workspaces).

At the time of writing (Feb 2023) Terra is working to expedite this process for Terra users; we recommend checking the [relevant Terra documentation](https://support.terra.bio/hc/en-us/articles/360029071251#h_01FFNCK82NB0YMAH5BTP41GYSY) for the latest information as well as recommendations about how to fill out the form.

# Notify Terra

Contacting Terra ahead of your class time helps the Terra team avoid any major disruptions to your class. Contact Terra by [submitting a request](https://support.terra.bio/hc/en-us/requests/new) for a hold on scheduled maintenance and downtime. It’s also a good idea to ask about major changes planned for the time prior to your class.

# Create Student Group {#student-group}

Creating a Group for your students will let you easily manage the class as a whole by granting the Group access to Billing Projects and Workspaces.

You will need a unique name for your Group. We suggest a combination of institution-class-role-term (e.g., `jhu-bio101-students-2023FA`). Only letters, numbers, underscores, and dashes are allowed in Group names.

## Create Terra Group

To create a Group:

::::{.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_terra_group_create.Rmd",
  branch = "add-terra-groups-modules",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

You now have a unique **student Group**.

## Add Instructors to Group

Now that your student Group has been created, you should add any additional instructors / course coordinators as **Admins**.  This will give them permission to add and remove students, in case you are unavailable.

To add someone to your group:

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_terra_group_add_member.Rmd",
  branch = "add-terra-groups-modules",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::


# Creating and adding student accounts

Since Terra operates on Google Cloud Platform, students need a Google account to make sure you can keep track of any computing costs they accrue. 

## Have students create a Google Account

```{r, child=c("_child_create_google_account.Rmd")}
```

## Have students sign in to Terra

Students need to sign into Terra with their Google account to allow you the  instructor to add them to projects and/or Workspaces associated with your specific class. This is the only way students can launch applications and perform computations on AnVIL. Have students [launch Terra](https://anvil.terra.bio/), and they should be prompted to sign in with your Google account.

::: {.warning}
**Collect Accounts**: It is _very important_ students share the Google account they used above with you! Otherwise, you cannot add them to billing projects, groups, or Workspaces.
:::

Students can always access Terra by going to [`anvil.terra.bio`](https://anvil.terra.bio/), or by clicking the link on the AnVIL home page.

```{r, echo=FALSE, fig.alt='Screenshot of the AnVIL home page. The button to "launch Terra" is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1tyt8ifxD3y7QW3nN27jh02aPrBvNEo1GN_u2Ne_UngM/edit#slide=id.gde7783227e_0_31")
```

# Groups for easy management

### Add Instructors as "Admin" (Student Group)

The next steps ensure any additional co-instructors and teaching assistants are able to administer the student Group in case you are unavailable. Follow the steps below to add each co-instructor in the student Group:

1. Go to https://anvil.terra.bio/#groups/ and click on the student Group name. This page should be visible at `https://anvil.terra.bio/#groups/<group-name>`.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group, and the specific Group that was just created. The student Group name is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g10118383b73_193_8")
    ```

1. Click on “+Add User”. You will be prompted to add the instructor’s AnVIL ID. 

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page for the specific Group that was just created. The "+Add User" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_104")
    ```

1. Type in the instructor’s AnVIL ID

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The instructor`s AnVIL ID, instructor-1@gmail.com, has been entered and the AnVIL ID (email) is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_58")
    ```

1. Make sure “Can manage users (admin)” is **selected**

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The instructor`s AnVIL ID, instructor-1@gmail.com, has been entered and the checkbox "Can manage users (admin)" has been selected and is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_65")
    ```

1. Click ADD USER. This will take you back to the Group administration page.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The instructor`s AnVIL ID, instructor-1@gmail.com, has been entered and the "ADD USER" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_71")
    ```

Make sure the newly added instructor displays “Admin” under “Roles” beside their AnVIL ID. Repeat this process for any additional co-instructors and teaching assistants.

```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the student Group that was just created, where the newly added instructor is visible in the user list. The instructor`s AnVIL ID, instructor-1@gmail.com is visible next to the role "Admin", which is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_87")
```

### Add Students as "Member"

Follow the steps below to add individual students to the student Group:

1. Go to https://anvil.terra.bio/#groups/ and click on the student Group name. This page should be visible at `https://anvil.terra.bio/#groups/<group-name>`.

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group, and the specific Group that was just created. The student Group name is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g10118383b73_193_8")
    ```

1. Click on “+Add User”. You will be prompted to add an AnVIL ID. 

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page for the specific Group that was just created. The "+Add User" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_104")
    ```

1. Type in the student’s AnVIL ID

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The student`s AnVIL ID, student-1@gmail.com, has been entered and the AnVIL ID (email) is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_111")
    ```

1. Click ADD USER

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the specific Group that was just created, with "Add user to Terra Group" pop out box. The student`s AnVIL ID, student-1@gmail.com, has been entered and the "ADD USER" button is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_117")
    ```

Make sure the newly added student displays “Member” under “Roles” beside their AnVIL ID. At present, each student’s AnVIL ID must be added separately.

```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group for the student Group that was just created, where the newly added student is visible in the user list. The student`s AnVIL ID, student-1@gmail.com is visible next to the role "Member", which is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_125")
```

Your instructor and student Groups are now set up.

## Group Email Lists

Note that your newly created Groups have Group emails associated with them. Take note of these Group emails. You will use them for granting access to your class Billing Projects and Workspaces. It saves you from having to add or revoke access to students one by one.

```{r, echo=FALSE, fig.alt='Screenshot of the Terra Group page. Emails associated with newly formed Groups have been highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_96")
```

# Shutting Down
