# (PART\*) For Each Class {-}

# Class Setup

## Overview of Class Setup

This section will show you how to organize your class to make it easier to administer access to your content. You will need to have a list of who will be taking your class, such as a course roster or sign-up list, as well as a list of additional instructors or teaching assistants. You can make changes later, so the list of students need not be final.

## Identify Funding

### NHGRI STRIDES {#strides-funding}

Through the [STRIDES](https://datascience.nih.gov/strides) program, NHGRI makes funding available to new users of the AnVIL, in collaboration with the [NIH Office of Data Science Strategy](https://datascience.nih.gov/about/odss). NHGRI currently supports the [AnVIL Cloud Credits Program (AC2)](https://anvilproject.org/news/2021/04/12/announcing-anvil-cloud-cost-credits-program) and will have a second round of funding available in fall of 2021.

## Collect Google IDs

AnVIL IDs are based on [Google accounts](account-setup.html#google-account).

Students -- Contact students/participants to get their AnVIL IDs. These should be Gmail addresses or emails with GSuite capabilities. You can link students to [Student Account Setup](student-account-setup.html) for instructions on what they should do.

Co-instructors -- If you will be working with other instructors, such as co-instructors or teaching assistants, you will need to collect their IDs as well.

## Set Up Billing Projects

Billing Projects in Terra help organize your compute costs. We suggest creating two different billing projects under the appropriate Billing Account that you created on `cloud.google.com`: one for students and one for co-instructors.

Billing Projects must be globally unique and cannot exceed 30 characters. We suggest a combination of institution-class-role (e.g., "jhu-bmr2021-instructors-bill-1"). To create a Billing Project for instructors:

1. Go to https://anvil.terra.bio/#billing

1. Click “+CREATE”

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing page. The "+CREATE" button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_88")
    ```

1. Type in your instructor Billing Project name

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing page with Create Billing Project popout box. The new billing project name, jhu-bmr2021-instructors-bill-1, is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_98")
    ```
    
1. Select the appropriate Billing Account

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing page with Create Billing Project popout box. The appropriate billing account name, My Billing Account, is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_2")
    ```
    
1. Click “CREATE BILLING PROJECT”

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing page with Create Billing Project popout box. The "CREATE BILLING PROJECT" button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_9")
    ```
    
You now have a unique **Instructor Billing Project**.

Next, create a student Billing Project. Again, we suggest a combination of institution-class-role (e.g., “jhu-bmr2021-students-bill-1”). To create a Billing Project for students:

1. Go to https://anvil.terra.bio/#billing 

1. Click “+CREATE”

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing page. The "+CREATE" button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.gdb96a00840_0_88")
    ```
    
1. Type in your student Billing Project name

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing page with Create Billing Project popout box. The new billing project name, jhu-bmr2021-students-bill-1, is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_15")
    ```
    
1. Select the appropriate Billing Account (same as above)

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing page with Create Billing Project popout box. The appropriate billing account name, My Billing Account, is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_21")
    ```

1. Click “CREATE BILLING PROJECT”

    ```{r, echo=FALSE, fig.alt='Screenshot of the Terra Billing page with Create Billing Project popout box. The "CREATE BILLING PROJECT" button is highlighted.'}
leanbuild::include_slide("https://docs.google.com/presentation/d/1HHWg47Tg6miv_K7GNB6ZDTx-4Jc5IMl7APfFtD1Rqag/edit#slide=id.g100474897dd_0_27")
    ```

You now have a unique **Student Billing Project**.
   
## Set Up Permissions

### Create Groups

<!-- To manage group permissions for Instructors versus students -->

### Add Additional Instructors as "Owner"

<!-- To Instructor Group -->

### Add Students as "Reader"

<!-- to Student Group -->

### Set Permissions

<!-- Set Instructor and Student permissions for Workspace and Terra Billing Projects -->

## Notify Terra

<!-- Request no scheduled maintenance downtime / ask about major changes -->
