# (PART\*) Student Instructions {-}

# Overview

The following chapters are aimed at students and provide instructions on how to sign up and access materials on AnVIL.

- If you are teaching an activity from the GDSCN or AnVIL collections, there may be more specific student instructions available in those books.
- If you are using your own materials, the instructions below should be sufficiently general.

# Setup AnVIL Account {#student-account-setup}

The following instructions will walk you through setting up an account so that you can carry out data analysis in the cloud.

<br>

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
cow::borrow_chapter(
  doc_path = "child/_child_student_create_account.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

# Access Materials {#student-clone-workspace}

The following instructions will show you how to access materials (tools and data) on AnVIL.

<br>

:::: {.borrowed_chunk}
```{r, echo = FALSE, results='asis'}
billing_project <- "provided by your instructor"
cow::borrow_chapter(
  doc_path = "child/_child_student_workspace_clone.Rmd",
  repo_name = "jhudsl/AnVIL_Template"
)
```
::::

# Open Galaxy

Coming soon!

# Open RStudio

Opening soon!
