# (APPENDIX) Appendix {-}

# Student Account Setup

AnVIL uses [Terra](https://anvil.terra.bio/) to run analyses. Terra operates on Google Cloud Platform, so you’ll need a Google account to make sure your instructor can keep track of any computing costs you accrue. 

## Step 1: Create a Google Account

```{r, child=c("_child_create_google_account.Rmd")}

```

## Step 2: Sign in to Terra

You need to sign into Terra with your Google account to allow your instructor to add you to projects and/or Workspaces associated with your specific class. This is the only way you can launch applications and perform computations on AnVIL. [Launch Terra](https://anvil.terra.bio/), and you should be prompted to sign in with your Google account.

You can always access Terra by going to [`anvil.terra.bio`](https://anvil.terra.bio/), or by clicking the link on the AnVIL home page.

```{r, echo=FALSE, fig.alt='Screenshot of the AnVIL home page. The button to "launch Terra" is highlighted.'}
ottrpal::include_slide("https://docs.google.com/presentation/d/1tyt8ifxD3y7QW3nN27jh02aPrBvNEo1GN_u2Ne_UngM/edit#slide=id.gde7783227e_0_31")
```

## Step 3: Share your ID

It is _very important_ that you share the Google account you used above with your instructor! Otherwise, they cannot add you to class projects or Workspaces.
